Data Specialization for a Staged Lambda Calculus

### 2015-02-27 paper/semantics.tex
blending 3.1

\crem{does this remark go anywhere?}

Thus, if we are willing to change the evaluation order of the
language (and evaluate under the \texttt{case} statement), it should
be possible to force \emph{all} the computations involving \texttt{l}
to be performed before \emph{any} of the computations involving
\texttt{k}.

@@

\paragraph{First-stage evaluation at \bbtwo\ ($\redtwosym$).}
Since terms at world \bbtwo\ represent second-stage computations, we should not
evaluate them yet. However, we do need to evaluate any first-stage computations
they contain (inside $\prev$), even if those computations are underneath
binders.

>>>>

@@

\paragraph{First-stage evaluation at \bbtwo\ ($\redtwosym$).}
Since terms at world \bbtwo\ represent second-stage computations, we should not
evaluate them yet. However, we do need to evaluate any first-stage computations
they contain (inside $\prev$), \emph{even if} those computations are guarded or
underneath binders.
